---
title: Ape (Gorilla,Chimpanzee \& Orang-utan) Face-shape (Male vs. Female) Bayesian
  Procrusts Analysis using R package ``BPviGM1" \& Conclusion
author: "Debashis Chatterjee"
date: "11/11/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
\section{Gorilla}
\subsection{Load the Landmark Data of Gorilla}

```{r}
require(shapes)
data(gorf.dat)
data(gorm.dat)
```

```{r}
ogf=gf=gorf.dat
ogm=gm=gorm.dat
```

```{r}
plotshapes(gm[,,1],joinline=c(1,6,7,8,2,3,4,5,1), col=1:8, symbol=1:8)
#polygon(gm[,1,1],gm[,2,1])
```

\subsection{Check for proper dimension of 3D array}
```{r}
dim(ogm)
```

\subsection{Sort according to Landmark order}

```{r}
sortcoldat=function(dat,seq)
{dat[,,]=dat[seq,,]
  return(dat)
}
```

```{r}
o.gf=ogf=sortcoldat(ogf,c(1,6,7,8,2,3,4,5))
o.gm=ogm=sortcoldat(ogm,c(1,6,7,8,2,3,4,5))
```


\subsection{Keep the data in Pre-shape space}

```{r}
require(Morpho)
for(k in 1:dim(ogf)[3])
{  o.gf[,,k]=rotonto(ogf[,,1],ogf[,,k],scale=T)$yrot 
}

for(k in 1:dim(ogm)[3])
{ o.gm[,,k] <-rotonto(ogm[,,1],ogm[,,k],scale=T)$yrot 
}

```

```{r}
plot(c(min(o.gm[,1,])-30, 100+max(o.gm[,1,])), c(min(o.gm[,2,])-30, max(o.gm[,2,])+30), type = "n", main="Raw Data-plot of Apes: male & female", xlab="x",ylab="y")
#plotshapes(gm[,,1],joinline=c(1,6,7,8,2,3,4,5,1), col=1:8, symbol=1:8)

polygon(o.gm[,1,1],o.gm[,2,1],density=0, col="skyblue", border="blue")
points(o.gm[,1,1],o.gm[,2,1], col="blue",pch=1:8)
polygon(o.gf[,1,1],o.gf[,2,1],density=0, col="pink", border="red")
points(o.gf[,1,1],o.gf[,2,1], col="red",pch=1:8)
```


\subsection{Load the novel R package BPviGM1}

```{r}

#install.packages("githubinstall")
#require(githubinstall)
#githubinstall("BPviGM1")

#install.packages("devtools")
#require(devtools)
#install_github("debashischatterjee111/BPviGM1")


```


\subsection{Start \& Run MCMC for Gorilla Male upto 10 objects}
```{r}
require(BPviGM1)
apem10000.10=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gm[,,1:10],10000)
```

```{r}
PPLOTpostvar2D(apem10000.10, 1000)
```

\subsection{Start \& Run MCMC for Gorilla Male upto 20 objects}

```{r}
apem10000.20=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gm[,,1:20],10000)
```
```{r}
PPLOTpostvar2D(apem10000.20, 1000)
```


\subsection{Start \& Run MCMC for Gorilla Male upto 30 objects}

```{r}
apem10000.30=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gm[,,],10000)
```

```{r}
PPLOTpostvar2D(apem10000.30, 1000)
```

\subsection{Start \& Run MCMC for Gorilla Female upto 10 objects}
```{r}
apef10000.10=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gf[,,1:10],10000)
```
```{r}
PPLOTpostvar2D(apef10000.10, 1000)
```

\subsection{Start \& Run MCMC for Gorilla Female upto 20 objects}

```{r}
apef10000.20=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gf[,,1:20],10000)
```
```{r}
PPLOTpostvar2D(apef10000.20, 1000)
```
\subsection{Start \& Run MCMC for Gorilla Female upto 30 objects}

```{r}
apef10000.30=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gf,10000)
```

```{r}
PPLOTpostvar2D(apef10000.30, 1000)
```


\subsection{Plot for Posterior Convergence of Gorilla Male}

```{r}

#plot(density(ress_10[1001:10000,2]), xlim=c(0,8),ylim=c(0,5),col="red",ylab="density (with vague prior)", xlab="Sample")
plot(density(apem10000.10), xlim=c(1,6),ylim=c(0,4),col="skyblue", xlab=expression(("Bayes Estimate of ")~~tilde(sigma)),ylab="MCMC Posterior Sigma Density",cex.main=1,main=expression(paste(bold("MCMC  posterior of APE (male)")~~tilde(sigma)~~("+ uniform prior"))))
#abline(v=theta, col="black",lwd=2, lty=1)
abline(v=mean(apem10000.30), col="darkblue",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.30), ylim=c(0,12),col="blueviolet")

legend("topleft",cex=0.6, c("n=10","n=20","n=30", expression(("(Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("skyblue","blue","blueviolet","darkblue"), lwd = c(1,1,1,1))
```


\subsection{Plot for Posterior Convergence of Gorilla Female}


```{r}

#plot(density(ress_10[1001:10000,2]), xlim=c(0,8),ylim=c(0,5),col="red",ylab="density (with vague prior)", xlab="Sample")
plot(density(apef10000.10), xlim=c(1,6),ylim=c(0,4),col="orange", xlab=expression(("Bayes Estimate of ")~~tilde(sigma)),ylab="MCMC Posterior Sigma Density",cex.main=1,main=expression(paste(bold("MCMC  posterior of APE (female)")~~tilde(sigma)~~("+ uniform prior"))))
#abline(v=theta, col="black",lwd=2, lty=1)
abline(v=mean(apef10000.30), col="red4",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apef10000.20), ylim=c(0,12),col="hotpink")
lines(density(apef10000.30), ylim=c(0,12),col="red")

legend("topright",cex=0.6, c("n=10","n=20","n=30", expression(("(Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("orange","hotpink","red","red4"), lwd = c(1,1,1,1))
```

\subsection{Combined-Plot for Shape-Variance Comparison Plot of Gorilla Female vs. Male}

```{r}
#COMBINED PLOT 

#plot(density(ress_10[1001:10000,2]), xlim=c(0,8),ylim=c(0,5),col="red",ylab="density (with vague prior)", xlab="Sample")
plot(density(apef10000.10[1000:10000]), xlim=c(1,7),ylim=c(0,5),col="orange", xlab=expression(("Bayes Estimate of ")~~tilde(sigma)),ylab="MCMC Posterior Sigma Density",cex.main=1,main=expression(paste(bold("MCMC  posterior of Variance: Gorilla (Male vs. female)")~~tilde(sigma)~~("+ uniform prior"))))
#abline(v=theta, col="black",lwd=2, lty=1)
abline(v=mean(apef10000.30), col="red4",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apef10000.20), ylim=c(0,12),col="hotpink")
lines(density(apef10000.30), ylim=c(0,12),col="red")

legend("topleft",cex=0.6,title="Ape (Female)", c("n=10","n=20","n=30", expression(("Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("orange","hotpink","red","red4"), lwd = c(1,1,1,1))
abline(v=mean(apem10000.30), col="darkblue",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.30), ylim=c(0,12),col="blue4")
lines(density(apem10000.10[1000:10000]), ylim=c(0,12),col="skyblue");
legend("topright",cex=0.6,title="Ape (Male)", c("n=10","n=20","n=30", expression(("Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("skyblue","blue","blue4","darkblue"), lwd = c(1,1,1,1))
grid()
```


\subsection{Conclusion}
It is being observed from posterior Face-shape  variance density  comparison-plot that there are Bayesian evidence for more face-shape variability in Gorilla male than the same for Gorilla Female. 





\section{Chimpanzee}




\subsection{Load the Landmark Data of Chimpanzee}

```{r}
require(shapes)
data(panf.dat)
data(panm.dat)
```

```{r}
ogf=gf=panf.dat
ogm=gm=panm.dat
```

```{r}
plotshapes(gm[,,1],joinline=c(1,6,7,8,2,3,4,5,1), col=1:8, symbol=1:8)
#polygon(gm[,1,1],gm[,2,1])
```

\subsection{Check for proper dimension of 3D array}
```{r}
dim(ogm)
```

\subsection{Sort according to Landmark order}

```{r}
sortcoldat=function(dat,seq)
{dat[,,]=dat[seq,,]
  return(dat)
}
```

```{r}
o.gf=ogf=sortcoldat(ogf,c(1,6,7,8,2,3,4,5))
o.gm=ogm=sortcoldat(ogm,c(1,6,7,8,2,3,4,5))
```


\subsection{Keep the data in Pre-shape space}

```{r}

for(k in 1:dim(ogf)[3])
{
  o.gf[,,k] <- rotonto(ogf[,,1],ogf[,,k],scale=T)$yrot 
}

for(k in 1:dim(ogm)[3])
{
  o.gm[,,k] <- rotonto(ogm[,,1],ogm[,,k],scale=T)$yrot 
}

```

```{r}
plot(c(min(o.gm[,1,])-30, 100+max(o.gm[,1,])), c(min(o.gm[,2,])-30, max(o.gm[,2,])+30), type = "n", main="Raw Data-plot of Apes: male & female", xlab="x",ylab="y")
#plotshapes(gm[,,1],joinline=c(1,6,7,8,2,3,4,5,1), col=1:8, symbol=1:8)

polygon(o.gm[,1,1],o.gm[,2,1],density=0, col="skyblue", border="blue")
points(o.gm[,1,1],o.gm[,2,1], col="blue",pch=1:8)
polygon(o.gf[,1,1],o.gf[,2,1],density=0, col="pink", border="red")
points(o.gf[,1,1],o.gf[,2,1], col="red",pch=1:8)
```


\subsection{Load the novel R package BPviGM1}

```{r}

#install.packages("githubinstall")
#require(githubinstall)
#githubinstall("BPviGM1")

#install.packages("devtools")
#require(devtools)
#install_github("debashischatterjee111/BPviGM1")


```


\subsection{Start \& Run MCMC for Chimpanzee Male upto 10 objects}
```{r}
require(BPviGM1)
apem10000.10=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gm[,,1:10],10000)
```
```{r}
PPLOTpostvar2D(apem10000.10, 1000)
```

\subsection{Start \& Run MCMC for Chimpanzee Male upto 20 objects}

```{r}
apem10000.20=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gm[,,1:20],10000)
```
```{r}
PPLOTpostvar2D(apem10000.20, 1000)
```


\subsection{Start \& Run MCMC for Chimpanzee Male upto 30 objects}

```{r}
apem10000.30=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gm[,,],10000)
```

```{r}
PPLOTpostvar2D(apem10000.30, 1000)
```

\subsection{Start \& Run MCMC for Chimpanzee Female upto 10 objects}
```{r}
apef10000.10=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gf[,,1:10],10000)
```
```{r}
PPLOTpostvar2D(apef10000.10, 1000)
```

\subsection{Start \& Run MCMC for Chimpanzee Female upto 20 objects}

```{r}
apef10000.20=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gf[,,1:20],10000)
```
```{r}
PPLOTpostvar2D(apef10000.20, 1000)
```
\subsection{Start \& Run MCMC for Chimpanzee Female upto 30 objects}

```{r}
apef10000.30=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gf,10000)
```

```{r}
PPLOTpostvar2D(apef10000.30, 1000)
```


\subsection{Plot for Posterior Convergence of Chimpanzee Male}

```{r}

#plot(density(ress_10[1001:10000,2]), xlim=c(0,8),ylim=c(0,5),col="red",ylab="density (with vague prior)", xlab="Sample")
plot(density(apem10000.10), xlim=c(1,6),ylim=c(0,4),col="skyblue", xlab=expression(("Bayes Estimate of ")~~tilde(sigma)),ylab="MCMC Posterior Sigma Density",cex.main=1,main=expression(paste(bold("MCMC  posterior of APE (male)")~~tilde(sigma)~~("+ uniform prior"))))
#abline(v=theta, col="black",lwd=2, lty=1)
abline(v=mean(apem10000.30), col="darkblue",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.30), ylim=c(0,12),col="blueviolet")

legend("topleft",cex=0.6, c("n=10","n=20","n=30", expression(("(Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("skyblue","blue","blueviolet","darkblue"), lwd = c(1,1,1,1))
```


\subsection{Plot for Posterior Convergence of Chimpanzee Female}


```{r}

#plot(density(ress_10[1001:10000,2]), xlim=c(0,8),ylim=c(0,5),col="red",ylab="density (with vague prior)", xlab="Sample")
plot(density(apef10000.10), xlim=c(1,6),ylim=c(0,4),col="orange", xlab=expression(("Bayes Estimate of ")~~tilde(sigma)),ylab="MCMC Posterior Sigma Density",cex.main=1,main=expression(paste(bold("MCMC  posterior of APE (female)")~~tilde(sigma)~~("+ uniform prior"))))
#abline(v=theta, col="black",lwd=2, lty=1)
abline(v=mean(apef10000.30), col="red4",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apef10000.20), ylim=c(0,12),col="hotpink")
lines(density(apef10000.30), ylim=c(0,12),col="red")

legend("topright",cex=0.6, c("n=10","n=20","n=30", expression(("(Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("orange","hotpink","red","red4"), lwd = c(1,1,1,1))
```

\subsection{Combined-Plot for Shape-Variance Comparison Plot of Chimpanzee Female vs. Male}

```{r}
#COMBINED PLOT 

#plot(density(ress_10[1001:10000,2]), xlim=c(0,8),ylim=c(0,5),col="red",ylab="density (with vague prior)", xlab="Sample")
plot(density(apef10000.10[1000:10000]), xlim=c(1,7),ylim=c(0,5),col="orange", xlab=expression(("Bayes Estimate of ")~~tilde(sigma)),ylab="MCMC Posterior Sigma Density",cex.main=1,main=expression(paste(bold("MCMC  posterior of Variance: Chimpanzee (Male vs. female)")~~tilde(sigma)~~("+ uniform prior"))))
#abline(v=theta, col="black",lwd=2, lty=1)
abline(v=mean(apef10000.30), col="red4",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apef10000.20), ylim=c(0,12),col="hotpink")
lines(density(apef10000.30), ylim=c(0,12),col="red")

legend("topleft",cex=0.6,title="Ape (Female)", c("n=10","n=20","n=30", expression(("Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("orange","hotpink","red","red4"), lwd = c(1,1,1,1))
abline(v=mean(apem10000.30), col="darkblue",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.30), ylim=c(0,12),col="blue4")
lines(density(apem10000.10[1000:10000]), ylim=c(0,12),col="skyblue");
legend("topright",cex=0.6,title="Ape (Male)", c("n=10","n=20","n=30", expression(("Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("skyblue","blue","blue4","darkblue"), lwd = c(1,1,1,1))
grid()
```


\subsection{Conclusion}
It is being observed from posterior Face-shape  variance density  comparison-plot that there are Bayesian evidence for more face-shape variability in Chimpanzee male than the same for Chimpanzee Female. 


\section{Orang-utan}



\subsection{Load the Landmark Data of Orang-utan}

```{r}
require(shapes)
data(pongof.dat)
data(pongom.dat)
```

```{r}
ogf=gf=pongof.dat
ogm=gm=pongom.dat
```

```{r}
plotshapes(gm[,,1],joinline=c(1,6,7,8,2,3,4,5,1), col=1:8, symbol=1:8)
#polygon(gm[,1,1],gm[,2,1])
```

\subsection{Check for proper dimension of 3D array}
```{r}
dim(ogm)
```

\subsection{Sort according to Landmark order}

```{r}
sortcoldat=function(dat,seq)
{dat[,,]=dat[seq,,]
  return(dat)
}
```

```{r}
o.gf=ogf=sortcoldat(ogf,c(1,6,7,8,2,3,4,5))
o.gm=ogm=sortcoldat(ogm,c(1,6,7,8,2,3,4,5))
```


\subsection{Keep the data in Pre-shape space}

```{r}

for(k in 1:dim(ogf)[3])
{
  o.gf[,,k] <- rotonto(ogf[,,1],ogf[,,k],scale=T)$yrot 
}

for(k in 1:dim(ogm)[3])
{
  o.gm[,,k] <- rotonto(ogm[,,1],ogm[,,k],scale=T)$yrot 
}

```

```{r}
plot(c(min(o.gm[,1,])-30, 100+max(o.gm[,1,])), c(min(o.gm[,2,])-30, max(o.gm[,2,])+30), type = "n", main="Raw Data-plot of Apes: male & female", xlab="x",ylab="y")
#plotshapes(gm[,,1],joinline=c(1,6,7,8,2,3,4,5,1), col=1:8, symbol=1:8)

polygon(o.gm[,1,1],o.gm[,2,1],density=0, col="skyblue", border="blue")
points(o.gm[,1,1],o.gm[,2,1], col="blue",pch=1:8)
polygon(o.gf[,1,1],o.gf[,2,1],density=0, col="pink", border="red")
points(o.gf[,1,1],o.gf[,2,1], col="red",pch=1:8)
```


\subsection{Load the novel R package BPviGM1}

```{r}

#install.packages("githubinstall")
#require(githubinstall)
#githubinstall("BPviGM1")

#install.packages("devtools")
#require(devtools)
#install_github("debashischatterjee111/BPviGM1")


```


\subsection{Start \& Run MCMC for Orang-utan Male upto 10 objects}
```{r}
require(BPviGM1)
apem10000.10=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gm[,,1:10],10000)
```
```{r}
PPLOTpostvar2D(apem10000.10, 1000)
```

\subsection{Start \& Run MCMC for Orang-utan Male upto 20 objects}

```{r}
apem10000.20=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gm[,,1:20],10000)
```
```{r}
PPLOTpostvar2D(apem10000.20, 1000)
```


\subsection{Start \& Run MCMC for Orang-utan Male upto 30 objects}

```{r}
apem10000.30=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gm[,,],10000)
```

```{r}
PPLOTpostvar2D(apem10000.30, 1000)
```

\subsection{Start \& Run MCMC for Orang-utan Female upto 10 objects}
```{r}
apef10000.10=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gf[,,1:10],10000)
```
```{r}
PPLOTpostvar2D(apef10000.10, 1000)
```

\subsection{Start \& Run MCMC for Orang-utan Female upto 20 objects}

```{r}
apef10000.20=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gf[,,1:20],10000)
```
```{r}
PPLOTpostvar2D(apef10000.20, 1000)
```
\subsection{Start \& Run MCMC for Orang-utan Female upto 30 objects}

```{r}
apef10000.30=MCMCpostPsample2D(1.5,
rep(0.5,1),o.gf,10000)
```

```{r}
PPLOTpostvar2D(apef10000.30, 1000)
```


\subsection{Plot for Posterior Convergence of Orang-utan Male}

```{r}

#plot(density(ress_10[1001:10000,2]), xlim=c(0,8),ylim=c(0,5),col="red",ylab="density (with vague prior)", xlab="Sample")
plot(density(apem10000.10), xlim=c(1,6),ylim=c(0,4),col="skyblue", xlab=expression(("Bayes Estimate of ")~~tilde(sigma)),ylab="MCMC Posterior Sigma Density",cex.main=1,main=expression(paste(bold("MCMC  posterior of APE (male)")~~tilde(sigma)~~("+ uniform prior"))))
#abline(v=theta, col="black",lwd=2, lty=1)
abline(v=mean(apem10000.30), col="darkblue",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.30), ylim=c(0,12),col="blueviolet")

legend("topleft",cex=0.6, c("n=10","n=20","n=30", expression(("(Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("skyblue","blue","blueviolet","darkblue"), lwd = c(1,1,1,1))
```


\subsection{Plot for Posterior Convergence of Orang-utan Female}


```{r}

#plot(density(ress_10[1001:10000,2]), xlim=c(0,8),ylim=c(0,5),col="red",ylab="density (with vague prior)", xlab="Sample")
plot(density(apef10000.10), xlim=c(1,6),ylim=c(0,4),col="orange", xlab=expression(("Bayes Estimate of ")~~tilde(sigma)),ylab="MCMC Posterior Sigma Density",cex.main=1,main=expression(paste(bold("MCMC  posterior of APE (female)")~~tilde(sigma)~~("+ uniform prior"))))
#abline(v=theta, col="black",lwd=2, lty=1)
abline(v=mean(apef10000.30), col="red4",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apef10000.20), ylim=c(0,12),col="hotpink")
lines(density(apef10000.30), ylim=c(0,12),col="red")

legend("topright",cex=0.6, c("n=10","n=20","n=30", expression(("(Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("orange","hotpink","red","red4"), lwd = c(1,1,1,1))
```

\subsection{Combined-Plot for Shape-Variance Comparison Plot of Orang-utan Female vs. Male}

```{r}
#COMBINED PLOT 

#plot(density(ress_10[1001:10000,2]), xlim=c(0,8),ylim=c(0,5),col="red",ylab="density (with vague prior)", xlab="Sample")
plot(density(apef10000.10[1000:10000]), xlim=c(1,7),ylim=c(0,5),col="orange", xlab=expression(("Bayes Estimate of ")~~tilde(sigma)),ylab="MCMC Posterior Sigma Density",cex.main=1,main=expression(paste(bold("MCMC  posterior of Variance: Orang-utan (Male vs. female)")~~tilde(sigma)~~("+ uniform prior"))))
#abline(v=theta, col="black",lwd=2, lty=1)
abline(v=mean(apef10000.30), col="red4",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apef10000.20), ylim=c(0,12),col="hotpink")
lines(density(apef10000.30), ylim=c(0,12),col="red")

legend("topleft",cex=0.6,title="Ape (Female)", c("n=10","n=20","n=30", expression(("Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("orange","hotpink","red","red4"), lwd = c(1,1,1,1))
abline(v=mean(apem10000.30), col="darkblue",lwd=2, lty=3)
#lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.20), ylim=c(0,12),col="blue")
lines(density(apem10000.30), ylim=c(0,12),col="blue4")
lines(density(apem10000.10[1000:10000]), ylim=c(0,12),col="skyblue");
legend("topright",cex=0.6,title="Ape (Male)", c("n=10","n=20","n=30", expression(("Bayes Estimate of ")~~tilde(sigma))), lty = c(1,1,1,3), col = c("skyblue","blue","blue4","darkblue"), lwd = c(1,1,1,1))
grid()
```


\subsection{Conclusion}
It is being observed from posterior Face-shape  variance density  comparison-plot that there are Bayesian evidence for more face-shape variability in Orang-utan male than the same for Orang-utan Female. 

\section{Conclusion: overall}
Based on the data "apes" (documented in R package "shapes"),and, after running a Bayesian procrusts analysis with R package "BPviGM1"), we observe from posterior Face-shape  variance density  comparison-plot that there are Bayesian evidence for more face-shape variability in all 3 apes (Gorilla, Chimpanzee,Orang-utan) male than the same for Orang-utan Female. Hence, we recommend extensive future research on this hypothesis.


